---
title: "imcarlyy_OriginalHomeworkCode_01"
author: "Carla Rojas"
date: 02.06.2025
output: 
  prettydoc::html_pretty 
---
if (!requireNamespace("stringr", quietly = TRUE))
  install.packages("stringr")

library(stringr)

**#CHALLENGE 1**

*#First step: Create a vector*
```{r echo=TRUE}
sentence <- "Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
sentence
```

*#Second step: Remove the punctuation from this sentence.*
```{r echo=TRUE}
sentencewno_punctiation <- gsub("[[:punct:]]","",sentence)
sentencewno_punctiation
```

*#Third step: Split the clean sentence (with no punctuation) into words (vectors)*
```{r echo=TRUE}
splited_sentence <- strsplit(sentencewno_punctiation," ")[[1]]
splited_sentence
```

*#Fourth step:Extract every 3rd word from the vector*
```{r echo=TRUE}
every_3rd_element <- splited_sentence[seq(3, length(splited_sentence), by = 3 ) ]
every_3rd_element
```

**#CHALLENGE 2**

#You are given a matrix for this first. Look below:
```{r echo=TRUE}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```
#First step: Given the matrix, m, above, extract the 2nd, 3rd, and 6th columns and assign them to the variable x
```{r echo=TRUE}
x <- m[,c(2,3,6)]
x
```

#Second step: Given the matrix, m, above, extract the 6th to 8th row and assign them to the variable x
```{r echo=TRUE}
x <- m[6:8,]
x
```
#Third step: Given the matrix, m, above, extract the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x
```{r echo=TRUE}
x <- m[2:6,2:9]
x
```

**#CHALLENGE 3**

#First step: Construct a 4-dimensional, 400 element array (5 x 5 x 4 x 4) named a consisting of the numbers 400 to 1 (i.e., a descending series)
```{r echo=TRUE}
a <- array(seq(400, 1), dim = c(5, 5, 4, 4))
a
```

#Second step: Given this matrix, what would the following return? a[1, 1, 1, 2]
```{r echo=TRUE}
a[1, 1, 1, 2] 
```

#Third step: Given this matrix, what would the following return? a[2, 3, 2, ]
```{r echo=TRUE}
a[2, 3, 2, ]
```

#Fourth step: Given this matrix, what would the following return? a[1:5, 1:5, 3, 3]
```{r echo=TRUE}
a[1:5, 1:5, 3, 3]
```

**#CHALLENGE 4**
#First step: Create a list representing this (simplified) primate taxonomy. 
# -Primates
#   Haplorhini
#     Anthropoidea
#       Platyrrhini
#         Cebidae
#         Atelidae
#         Pitheciidae
#       Catarrhini
#         Cercopithecidae
#         Hylobatidae
#         Hominidae
#     Tarsioidea
#       Tarsiidae
#
#   Strepsirhini
#     Lorisoidea
#       Lorisidae
#       Galagidae
#     Lemuroidea
#       Cheirogaleidae
#       Lepilemuridae
#       Indriidae
#       Lemuridae
#       Daubentoniidae

#Creating the Strepsirhini list
```{r echo=TRUE}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
```

#Creating the Haplorhini list, first part
```{r echo=TRUE}
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Catarrhini, Platyrrhini)
names(Anthropoidea) <- list("Catarrhini", "Platyrrhini")
Anthropoidea
```

#Creating the Tarsioidea list (for the Haplorhini list)
```{r echo=TRUE}
Tarsioidea <- c("Tarsiidae")
names(Tarsioidea) <- list("Tarsiidae")
Tarsioidea
```

#Now, I'm making Tarsioidea and Anthropoidea be inside of Haplorhini
```{r echo=TRUE}
Haplorhini <- list(Tarsioidea, Anthropoidea)
names(Haplorhini) <- list("Tarsioidea", "Anthropoidea")
Haplorhini
```

#Here, I'm merging the Haplorhini and Strepsirhini list be in the big primates list
```{r echo=TRUE}
Primates <- list (Haplorhini, Strepsirhini)
names(Primates) <- list ("Haplorhini", "Strepsirhini")
print(Primates)
```

#**CHALLENGE 5**
#First step: Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.
```{r}
m3 <- matrix(data= c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow= 5, ncol= 3, byrow= TRUE)
m3
```
#Second part: Then, coerce the matrix to a data frame.
```{r}
dataframed_m3 <-as.data.frame(m3)
dataframed_m3
```

#Third part: As a data frame, coerce the second column to be logical-valued
```{r}
dataframed_m3[,2] <- as.logical(dataframed_m3[,2])
dataframed_m3
```

#Fourth part: As a data frame, coerce the third column to be factor-valued
```{r}
dataframed_m3[,3] <- as.factor(dataframed_m3[,3])
dataframed_m3
```

#Fifth step: When you are done, use the str() command to show the data type for each variable in your dataframe.
```{r}
str(dataframed_m3)
```


*#Challenge number 1 faced throughout this homework:*
#1. Learning and understand the code needed to extract every 'certain number of elements' from a vector. In this case, my fourth step, in Challenge one, had that code. I knew that this code was important for future projects that would have even greater amounts of elements. However, due to complexity of the code, it took me a long time to fully understand it and use it. I still feel like I don't know it by memory, but now I feel confident enough to figure it out after taking a look at it. I used google to understand each part of the code as well. 

*#Challenge number 2 faced throughout this homework:*
#One of the things I had to deal with doing this homework was when I made matrices. For some reason, my R program was defaulted in a way that the console width was only up to 80, instead of 100. So when I created the matrix for Challenge 2, Module 4, the output that I would see would be 9 columns next to each other, and the 10th one, at the bottom of them all. After googling this information, I also learned that by using the following code, I could set the console width: 

#First, set it with this code: options(width = 100)
#Second, create your matrix. Mine was this one: 
#     m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
#     m 

#Challege number 3 faced throughout this homework:*
#On challenge 4, I had to work for at least 3 hours on my code to create the Primate's taxonomy. Again, working with a lot of numbers, words and symbols made everything very confusing and a little overwhelming for me. Also, understanding how to create the code in a way that showed the taxonomy in order, and with the proper subdivisions, was hard. I believe that my code is correct, but I'm sure there might be another way of writing it that makes it look a little more understandable and smooth. 

*#Challenge number 4 faced throughout this homework:*
#Overall, one of the things that I struggled with a lot, and that made things harder and longer for me was the misspelling/overwriting. I kept making a lot of mistakes and getting a lot of frustrating 'error' messages that, after checking my code for hours, ended up being a misspelling issue. Again, with the amount of things that I had to run here, I felt like this was common. The only thing that I learned from this was to check my words when running a code and getting an 'error' message. That made things easier at the end because I would take my time to check my codes first, and then see if that was the problem, before checking anything else. At the beginning, on the contrary, I would only think that it was my code's method and delete everything to run it all again :( 

*#Challenge number 5 faced throughout this homework:*
#The language barrier, both in R and English, made this homework three times more difficult. I sometimes wouldn't understand the coding language, and in other ocassions, I would just not understand the explanation/request from the module. I think that this is normal and although is not a problem that I can solve overnight, I did started doing some things that could help me throughout the homeworks, like a vocabulary sheet with all the unknown terms, or an additional doc with all the work I've done in this homework + EXTRA tiny details, in case I forget how I did it/what it meant. 

